
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Design and Development of a Multi-Vendor E-Commerce Marketplace}

\author{Nadim Jebali}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{National Engineering Diploma in Applied Sciences and Technology}
% TODO(confirm): speciality / filière — sensible default used below.
\speciality{Software Engineering}

%% Professional supervisor
\proFramerName{Mr. Mohammed Aziz Chibani}
% TODO(confirm): professional supervisor's exact title.
\proFramerSpeciality{Software Engineer}

%% Academic supervisor
\academicFramerName{Ms. Sawssen Jalel}
\academicFramerSpeciality{Lecturer}

%% Entreprise d'accueil
\companyName{NeuralBey}

%% Année universitaire
\collegeYear{2025 - 2026}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{I authorise the student to submit the internship report for a defence.}

\academicSignSentence{I authorise the student to submit the internship report for a defence.}

%%% FR
\frenchAbstract{Ce rapport présente la conception et le développement d'une place de marché électronique multi-vendeurs, réalisé dans le cadre d'un projet de fin d'études au sein de la société NeuralBey. La plateforme permet à des vendeurs indépendants d'ouvrir leurs propres boutiques, de publier des produits et de traiter des commandes au sein d'un environnement partagé et gouverné de façon centralisée, tandis que les administrateurs valident les vendeurs, modèrent le contenu et mettent en avant une sélection de qualité. Sa principale particularité est un pipeline de vérification assisté par l'intelligence artificielle qui contrôle automatiquement les boutiques et les produits afin de préserver la confiance des acheteurs à grande échelle, complété par un assistant conversationnel de base de données et une refonte de vitrine assistée par IA. Le système est bâti comme une application React monopage adossée à une API modulaire NestJS et une base de données MariaDB, n8n orchestrant les traitements d'intelligence artificielle, et il est livré au moyen d'une chaîne DevOps entièrement conteneurisée et décrite comme code (Docker, Terraform, GitHub Actions). Le projet a suivi une démarche agile Scrum répartie sur deux releases.}

\frenchAbstractKeywords{Place de marché multi-vendeurs, E-commerce, Intelligence Artificielle, NestJS, React, Scrum, DevOps}

%%% EN
\englishAbstract{This report presents the design and development of a multi-vendor e-commerce marketplace, carried out as a final-year engineering project at NeuralBey. The platform lets independent sellers open their own stores, publish products and fulfil orders within a shared, centrally-governed environment, while administrators onboard sellers, moderate content and curate featured selections. Its distinguishing feature is an AI-assisted verification pipeline that automatically screens stores and products to protect buyer trust at scale, complemented by a conversational database assistant and AI-assisted storefront redesign. The system is built as a React single-page application backed by a modular NestJS API and a MariaDB database, with n8n orchestrating the AI workflows, and is delivered through a fully containerised, infrastructure-as-code DevOps pipeline (Docker, Terraform, GitHub Actions). The project followed an agile Scrum approach spread over two releases.}

\englishAbstractKeywords{Multi-vendor marketplace, E-commerce, Artificial Intelligence, NestJS, React, Scrum, DevOps}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{false}

\companyEmail{contact@neuralbey.com}
\companyTel{71 111 111}
\companyFax{71 222 222}
\companyAddressAR{تونس}
\companyAddressFR{Tunis, Tunisie}
